Report on Late Winter2013 Production: Image Differencing\vspace{-2ex}

### 2013-03-30 W13report.tex
Removed a MOVE ME section.
Removing ambiguous conclusions.
new figures and updated text

When we look at the MSE per chip and compare with the minimum false positive config we 
find good agreement.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
even if the false positive rate is slightly higher.

However, the trends are encouraging and we will pursue these methods
in our future work with the more complicated simulations.

@@

\begin{table}
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
\hline
v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
\end{tabular}

\caption{Total number of false detections that we expect based on a
  4000x4072 pixel sensor.  This number is dependent on the seeing and
  detection threshold, so we list the values at a threshold of 4.5,
  5.0, and 5.5 sigma for the seeings in the 3 visits used in this
  production. We list the total number of positive {\it plus} negative
  detections; they should be present in equal quantities. The variance
  is as determined from Monte Carlo simulations.\label{tab-fp} }
\end{table}

\begin{table}
\centering
\begin{tabular}{clc|cccccc}
\hline
\multicolumn{9}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & N$_{Expect}$ & N$_{Measured}$ &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & N$_{-}$ / N$_{+}$ \\
\hline
v6866601 & True      & 108$\pm$27   & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
         & False     & $\cdots$     & 143     &51         & 92 & 2     & 11  & 0.4 \\
v6866602 & True      & 45$\pm$18    & 42      &36         & 6  & 2     & 1   & 2.6 \\
         & False     & $\cdots$     & 53      &45         & 8  & 2     & 1   & 0.5 \\
v6866603 & True      & 27$\pm$18    & 23      &23         & 0  & 1     & 0   & 2.8 \\
         & False     & $\cdots$     & 36      &35         & 1  & 1     & 0   & 3.4 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false detections (N$_{Measured}$).  N$_{Expect}$
  lists the total number we expect to detect as random fluctuations,
  from Table~\ref{tab-fp}, and are the same for pre and postfiltering.
  Whether a detection is a match or an orphan (N$_{Match}$ and
  N$_{Orphan}$) is determined using a 3'' match radius with the input
  reference catalog.  We list the number of background fluctuations
  that are expected to randomly associate with a Source N$_{Random}$,
  given the density of objects in the images and a 3'' match radius,
  assuming that N$_{Orphan}$ represents 96\% of the total population
  of detections from Gaussian fluctuations.  We also list the number
  of false detections that are found within the outer 100 pixels of
  the image N$_{D<100}$.  The final column lists ratios of the number
  of negatively detected false detections to those with positive
  flux. \label{tab-bestfp10}}
\end{table}

@@

>>>>

When we look at the MSE per chip and compare with the minimum false positive config we 
find good agreement, in general.  The findings are summarized in Table \ref{tab-MSE_persensor}.  Because
the MSE is sensitive to over fitting, we observe that it tends to lower complexity configs
even if the false positive rate is slightly higher.  We will continue working on this with more complicated simulations.

@@

\begin{table}
\centering
\begin{tabular}{lcccc}
\hline
\multicolumn{5}{|c|}{Theoretical Number of False Detections per Sensor} \\
\hline
Visit    & FWHM (pixels) & $\sigma=4.5$ & $\sigma=5.0$ & $\sigma=5.5$\\
\hline
v6866601 & 3.0 & 114$\pm$11 & 12$\pm$3& 1$\pm$1\\
v6866602 & 4.4 & 54$\pm$8 & 5$\pm$2& 0.5$\pm$0.5\\
v6866603 & 6.0 & 29$\pm$6 & 3$\pm$2&0.2$\pm$0.4\\
\end{tabular}
\caption{Total number of false detections that we expect based on
  a 4000x4072 pixel senser.  We list the total number of positive {\it plus} negative detections;
  they should be present in equal quantities. The variance is as determined from Monte Carlo simulations.\label{tab-fp}
}
\end{table}

\begin{table}
\centering
\begin{tabular}{clcccccc}
\hline
\multicolumn{8}{|c|}{Best Results: Production 10} \\
\hline
Visit    & Prefilter & Total False Detections &  N$_{Orphan}$ & N$_{Match}$ & N$_{Random}$ & N$_{D<100}$ & Nneg / Npos \\
\hline
v6866601 & True      & 70      &60         & 10 & 3     & 4   & 1.8 \\ 
         & False     & 143     &51         & 92 & 2     & 11  & 0.4 \\
v6866602 & True      & 42      &36         & 6  & 2     & 1   & 2.6 \\
         & False     & 53      &45         & 8  & 2     & 1   & 0.5 \\
v6866603 & True      & 23      &23         & 0  & 1     & 0   & 2.8 \\
         & False     & 36      &35         & 1  & 1     & 0   & 3.4 \\
\end{tabular}
\caption{Total number of {\tt DiaSources} detected at 5--sigma from
  all 9 sensors in raft 2,2, for the configurations that yielded the
  lowest number of false detections.  Matches are determined using a
  3'' match radius with the input reference catalog.  Objects with the
  {\tt EDGE} flag are ignored.  We list the number of background
  fluctuations that are expected to randomly associate with a Source
  N$_{Random}$, given the density of objects in the images and a 3''
  match radius, assuming that N$_{Orphan}$ represents 96\% of the
  total population of detections from Gaussian fluctuations.
  We also list the number of false detections that are found within
  the outer 100 pixels of the image N$_{D<100}$.  The final column
  lists ratios of the number of negatively detected false detections
  to those with positive flux, a 5--sigma. \label{tab-bestfp10}}
\end{table}

@@

\begin{table}
\centering
\begin{tabular}{clcccc}
\hline
\multicolumn{5}{|c|}{Per Sensor MSE Comparison} \\
\hline
Visit    & Prefilter & N$_{Same}$ & N$_{<3}$ & $\Delta FP$ & max($\Delta FP$)\\
\hline
v6866601 & True      & 0      & 2        & 22 & 4\\
         & False     & 4      & 6        & 24 & 10\\
v6866602 & True      & 3      & 5        & 7 & 2\\
         & False     & 6      & 7        & 8 & 6\\
v6866603 & True      & 6      & 7        & 3 & 1\\
         & False     & 6      & 8        & 3 & 1\\
\end{tabular}
\caption{
We exampine the configs chosen based on the minimum MSE and compare them to the config of the
minimum number of false positives.  The sample here consists of 9 sensors per visit.  
N$_{Same}$ is the number of times the minimum MSE coincides with the minimum false positives.  N$_{<3}$
is the number of times the minimum false positive config has an MSE in the minimum 3.  $\Delta FP$
is the total change in false positive count using the minimum MSE config as compared to the sum of the minimum 
false positives per sensor.  max($\Delta FP$) is the maximum change in detected false positives on any sensor in that visit.
\label{tab-MSE_persensor}}
\end{table}
